\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fontawesome}

\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Omar E. Mbye}} \\
    MSc in Mathematics (Statistics and Data Science) \\
    \faEnvelope\ omar.email@example.com \quad
    \faLinkedin\ linkedin.com/in/omar-mbye \quad
    \faGithub\ github.com/omar-mbye
\end{center}

\section*{Professional Summary}
Data Analyst with a strong foundation in statistical modeling, CPI analysis, and economic forecasting. Experienced in GARCH variants, panel data construction, and integrating climate shocks and governance indicators into macroeconomic models. Proficient in R, CSPro, and Survey Solutions, with a passion for data-driven policy research and digital transformation in LMICs.

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{MSc in Mathematics (Statistics and Data Science)}, University of The Gambia — 2025
    \item \textbf{Diploma in Statistics}, Indian Statistical Institute, Kolkata — 2022
    \item \textbf{BSc in Economics}, University of The Gambia — 2020
\end{itemize}

\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Statistical Modeling:} ARIMA, SARIMA, GARCH, EGARCH, GJR-GARCH
    \item \textbf{Programming:} R, Python (CS50AI), LaTeX
    \item \textbf{Survey Tools:} CSPro, Survey Solutions (skip logic, validation rules, rosters)
    \item \textbf{Data Integration:} CPI, climate data, governance indicators
    \item \textbf{Version Control:} GitHub
\end{itemize}

\section*{Experience}
\textbf{Statistician – Consumer Price Index}, Gambia Bureau of Statistics \\
\textit{Jan 2023 – Present}
\begin{itemize}[leftmargin=*]
    \item Analyzed CPI trends and constructed inflation models using GARCH variants.
    \item Integrated climate and governance data into panel datasets for LMICs.
    \item Designed and validated survey instruments using CSPro and Survey Solutions.
    \item Collaborated on digital transformation initiatives to improve data quality and accessibility.
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Thesis:} Inflation Volatility and Governance in LMICs — Developed panel models incorporating CPI, climate shocks, and governance indicators.
    \item \textbf{Portfolio:} Built reproducible forecasting models in R and documented workflows using LaTeX and GitHub.
\end{itemize}

\section*{Interests}
Community development, policy research, clinical trial design, AI and Python programming, think tank development.

\end{document}
